Response to Reviewers $Rev^1$

### 2020-04-08 ICT_Frontiers_rev202001.tex
Updates from Overleaf

        \linelabel{line:IC2CG}
		Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) 
		\begin{align}
		    J_{t}(E \rightarrow Y )=I(Y_{t+1};E_t|Y_t)
		\end{align}
		to the system-environment dependency
         and the micro-macro scale dependency
         \begin{align}
		    J_{t}(X \rightarrow Y )=I(Y_{t+1};X_t|Y_t)
		\end{align}  
         even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).

        With the two definitions we can state the main hypothesis of \ac{OurTheory}
        \begin{hypothesis}
        A process $Y$ is conscious if and only if it is a C-process of some process $X$. Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the C-process to the environment i.e. $NTIC_t(E\rightarrow Y)$:
        \begin{align}
            C_t^{Content} &= y_t \label{eq:cContent}\\
            C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
        \end{align}
        \end{hypothesis}

\begin{hypothesis}
        For any coarse-graining $Y$ of a stochastic process $X$, a refinement $S$ of $Y$ and the environment $E$ of $S$.  
        The \emph{content $C_t^{Content}(Y)$ of the consciousness of $Y$ at time $t$} is the state $y_t$ of $Y$ at time $t$ and \emph{the level $C_t^{Level}(Y)$ of the consciousness of $Y$} is the degree of NTIC of the C-process to the environment minus the information flow from the microscopic process $X$ to $Y$:
        \begin{align}
            C_t^{Content} &= y_t \label{eq:cContent}\\
            C_t^{Level} &= NTIC_t(E\rightarrow Y)-J_t(X \rightarrow Y) \label{eq:cLevel}
        \end{align}
        \end{hypothesis}

@@

            \subsubsection*{Processes that are not Informationally Closed}\label{sec:reflexive}
            \linelable{line:notIC}
            % \paragraph{@ Acer's version}
            % Based on Eq.~\ref{eq:nticObjective2}), to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}). For agents such as human being, who always face informationally rich environments, the environment is usually partially observable with limited sensory capacities. This leads to the sensor values are not deterministic (or close to it). In such cases, if the state of a internal process is mainly driven by sensory inputs, the information flow from the environment to the process is considered to be large and the process is not informationally closed.

            % First, to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}). Here, we illustrate two distinctive scenarios which shade light of the relationship between informational closure and consciousness. 
            % \paragraph{@ Martin's version}
            The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next. In this situation we can show that a system passively processing the observations (including copying them) achieves lower values of NTIC and therefore lower levels of consciousness than a system that is able to accurately predict the observations.

            %Is there a (generative) epsilon machine that achieves higher NTIC than copying? If yes, under what conditions (e.g. reversibility of the underlying environment process?) on the sensor process does it exist?
            %Is Bertschinger's system better than copying? 
            \ac{OurTheory} leads to some surprisingly simple conscious processes. Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and the system just copies the environment process. Then the system can achieve positive values of NTIC with respect to the environment. ICT states that such processes are conscious.

>>>>

        \noindent Note that, here we applied the same definitions of information flow (Eq.~\ref{eq:InformationFlow}) \linelabel{line:IC2CG}
        \begin{align}
            J_{t}(E \rightarrow Y )=I(Y_{t+1};E_t|Y_t)
        \end{align}
            to the system-environment dependency
            and the micro-macro scale dependency
        \begin{align}
            J_{t}(X \rightarrow Y )=I(Y_{t+1};X_t|Y_t)
        \end{align}  
        even though the Bayesian graphs are different in the two scenarios. Both of these settings have already been used in the literature \citep[see][]{BERTSCHINGER.2006, PFANTE.2014}).\\

        With the two definitions we can state the main hypothesis of \ac{OurTheory}
        \begin{hypothesis}
        A process $Y$ is conscious if and only if it is a C-process of some process $X$. Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the process to the environment i.e. $NTIC_t(E\rightarrow Y)$:
        \begin{align}
            C_t^{Content} &= y_t \label{eq:cContent}\\
            C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
        \end{align}
        \end{hypothesis}

        \begin{hypothesis}
        A process $Y$ is conscious if and only if it is a C-process of some process $X$. Also the content of consciousness $C_t^{Content}$ at time $t$ is the state $y_t$ of the C-process at time $t$ and the level of consciousness $C_t^{Level}$ is the degree of NTIC of the process to the environment i.e. $NTIC_t(E\rightarrow Y)$:
        \begin{align}
            C_t^{Content} &= y_t \label{eq:cContent}\\
            C_t^{Level} &= NTIC_t(E\rightarrow Y) \label{eq:cLevel}
        \end{align}
        \end{hypothesis}

        % \begin{hypothesis}
        %         For any coarse-graining $Y$ of a stochastic process $X$, a refinement $S$ of $Y$ and the environment $E$ of $S$.  
        %         The \emph{content $C_t^{Content}(Y)$ of the consciousness of $Y$ at time $t$} is the state $y_t$ of $Y$ at time $t$ and \emph{the level $C_t^{Level}(Y)$ of the consciousness of $Y$} is the degree of NTIC of the C-process to the environment minus the information flow from the microscopic process $X$ to $Y$:
        %         \begin{align}
        %             C_t^{Content} &= y_t \label{eq:cContent}\\
        %             C_t^{Level} &= NTIC_t(E\rightarrow Y)-J_t(X \rightarrow Y) \label{eq:cLevel}
        %         \end{align}
        %         \end{hypothesis}

@@

            \subsubsection*{Processes that are not Informationally Closed}\label{sec:reflexive}
             \linelabel{line:notIC}The first scenario is that of a system partially observing the environment in such a way that the current observation is insufficient to predict the next. In this situation we can show that a system passively processing the observations (including copying them) achieves lower values of NTIC and therefore lower levels of consciousness than a system that is able to accurately predict the observations. 
            % \paragraph{@ Acer's version}
            % Based on Eq.~\ref{eq:nticObjective2}), to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}). For agents such as human being, who always face informationally rich environments, the environment is usually partially observable with limited sensory capacities. This leads to the sensor values are not deterministic (or close to it). In such cases, if the state of a internal process is mainly driven by sensory inputs, the information flow from the environment to the process is considered to be large and the process is not informationally closed. 
            % First, to maximise NTIC, a process can minimise the information flow from the environment to the process $J_{t}(E \rightarrow Y ) := I(Y_{t+1};E_{t}|Y_{t})$ (Eq.~\ref{eq:InformationFlow}). Here, we illustrate two distinctive scenarios which shade light of the relationship between informational closure and consciousness. 
            % \paragraph{@ Martin's version}
            %Is there a (generative) epsilon machine that achieves higher NTIC than copying? If yes, under what conditions (e.g. reversibility of the underlying environment process?) on the sensor process does it exist?
            %Is Bertschinger's system better than copying? 
            \ac{OurTheory} leads to some surprisingly simple conscious processes. Consider the case already noted by \citet{BERTSCHINGER.2006} where the environment process is deterministic (or close to it) and the system just copies the environment process. Then the system can achieve positive values of NTIC with respect to the environment. ICT states that such processes are conscious.

### 2020-04-08 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

    	\begin{ans}
    		\newline
    		a) It is true it is true that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$. However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$. This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2. Therefore, only completely closed NTIC processes are consider as C-processes. 
    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\

@@

        \begin{ans}        	
            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes. In some cases such a definition would be more general than the present one for example when there is no final microscale and instead there is an infinite number of more and more microscopic scales. However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea. Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.   
            % For this We use the underlying $X$ with respect to $Y$ in order to illustrate the scale problem of consciousness. 
            % It ensures that the information transfer from all coarse-grainings of $X$ to $Y$ vanishes. Therefore, human conscious experiences do not involve information from other scales of coarse-graining. 
            % 
            To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e. $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$. So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
        \end{ans}

@@

        \begin{question}
            Exclusion or no exclusion? The authors state multiple times that "every process with a positive non-trivial information closure (NTCI) has consciousness." (p.3, and also p.12).
            a) Yet, Figure 4 is ambiguous in the sense that the maximum somehow seems important, while actually all levels should give rise to separate experiences. I don't see how ICT without something like exclusion (IIT style) would indicate that the maximum should correspond to human consciousness. It could just be any one out of many consciousnesses.
            b) p. 14: comparison to IIT: what does ICT say about different sets of variables at the same level. There might well be multiple ways to partition $X$ into S and E, with many overlapping S's. Would those all be conscious? They would not be informationally closed from each other but they could all fulfill the requirements in the Hypothesis. It seems like finding the maximum within a level over the possible sets of elements/variables is a necessary step to identify boundaries (I think also Krakauer does that across sets of variables, but not 100\% sure)        
        \end{question}

    	\begin{ans}
            We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does. 
            % This is a difference between IIT and ICT. \\
            % The exclusion criterion is based on the assumption that individual entities (e,g, consciousnesses) should share no subset with any other entities. Namely, within the boundary of an individual, we should not find any subset also belonging to other individuals. \\
            A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}. For example, \citet{krakauer2014information,krakauer2020information} proposed an algorithm to add and remove variables in order to find the boundary. \\
            It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those. All such subsets are thus conscious. However, while conscious, they are not necessarily the entire or whole consciousness. They may be part of a more extended consciousness. In order to find whole or entire consciousnesses we can use the algorithm in \citet{krakauer2014information, krakauer2020information}. This algorithm adds variables to or removes variables from the system if this results in a reduction of transfer entropy from the corresponding environment. This means that whole consciousnesses are maximally closed subsets of variables. We currently do not know if such maxima also are maxima of NTIC. We also currently do not know whether multiple such whole consciousnesses can overlap or not and will accept either case within ICT. In this way either exclusion emerges from our definitions or not.

            % if a subset is not informationally closed the subset is considered as a part of the system.
            % ICT applies the same notion to consciousness. A subprocess (partition) of a conscious (NTIC) process can have a positive value of NTIC, and therefore, is conscious. However, the subprocess is not "another conscious process". Instead, it is considered as a subspace of the consciousness. Namely, the information contributed from the subprocess corresponds to a part of the whole conscious experience. \\
            This is also why ICT allowed the existence of multiple consciousnesses across the scales of coarse-graining. Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero). This is in line with using informational closure in level identification \citep{PFANTE.2014} . \\
            % Therefore, ICT without exclusion criterion can parsimoniously explain the individuality of consciousness within and across the scale of coarse-graining.
            \todo{Maybe add something in the manuscript}
% 			We do not impose the exclusion criterion in ICT. Instead, the concept of informational closure already involves the notion of identifying the boundary of a system.

% 			 system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014}

% 			That human consciousness constitutes a maximum is a conjecture at the moment. Humans are of course very good at predicting their future experiences and (apart from multiple humans together) we are not aware of systems that are better. This is the only reason why we think human consciousness constitutes a maximum. We accept that there can be many other overlapping conscious systems. Concerning multiple possible partitions, \citet{krakauer2014information} propose an algorithm to add and remove variables in order to find a maximum. This could be used to find a maximum and something like a boundary of the maximum. Maxima are of course interesting but we don't see why they should exclude anything.   Instead, the concept of informational closure already involves the notion of individuality and was used to identify the system-environment distinction \citep{BERTSCHINGER.2006} and level identification \citep{PFANTE.2014} in systems theory (however not completely, please see our discussion at Line \lineref{line:individuality}).

% 			It is true that if we assume a process $Y$ is NITC with respect to $E$. Every subset of $Y$ can have different degrees of NTIC with respect to $E$ as well. However, it is important to note that the subsets are not "other consciousnesses". Rather, they are subspaces of this conscious process $Y$.

% 			\toWrite{I this this is still bad}

%			\textit{If we sample a subset of elements, if its closedness is lower than 
%			Consider a simplified case, a process $Y$ is NITC with respect to $E$. 
%			For Any subset of 
%			A partition of $Y$ is a set $P_y$ which divides $Y$ into two subsets $P_y=\{Y_1, Y_2\}$. }    		    		    		
    	\end{ans}

@@

        \begin{ans}
        	The reviewer is right. Feed-forward networks can be conscious under ICT. Similarly, a video camera can achieve positive levels of NTIC and, therefore, be conscious. We have worked extensively on Section 5 to make this clear (see from Line:~\lineref{line:notIC}).
        	There we have weakened multiple claims involving a clear conscious to unconscious distinction to claims about differences between levels of consciousness. 
        	Concerning the camera example we can show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image and the next there are systems that achieve higher NTIC. 
        	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.

@@

	   % @ The reviewer is correct about the video camera example under the condition that the environment past state $E_{t-1}$ shares information with its current state $E_t$, i.e., $I(E_{t-1}, E_t)>0$.

	   % @ In such case, simply copying environmental states to a process can lead to positive NTIC.

	   % @ In fact, this is one way to achieve NTIC discribed in \cite[p.~4]{BERTSCHINGER.2006},    
	   % \begin{quote}
	   % 	\textit{"B1)~Passive adaptation: The system is driven by the environment and adapts passively to all changes in the environment. In the case of an environment, that appears deterministic to the system, $H(\hat{e}_{n+1} |\hat{e}_n)=0$, this can be achieved by simply copying the observation of the environment into the system, $S_{n+1} = \hat{e}_n$."}        
	   % \end{quote}

@@

    	\begin{ans}
	    	We want to emphasise that not all the processes in the neural system are NTIC processes. This is evident since some processes in the neural system are not informationally closed. They only passively react to sensory inputs or other processes of the neural system.

	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment. This notion is shortly indicated at line \lineref{line:neu-env} in our original manuscript. There is no doubt that these processes are still active during sleep and dreaming. We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e. other parts of the neural system.  However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our manuscript. However, we thank the reviewer for bringing up this important question. We believe that this is still worth mentioning. We have added a short paragraph as follows:

>>>>

    	\begin{ans}
    		\newline
    		a) It is true it is true that the information flow term $J_t(E\rightarrow Y)$ does not have to be zero for $NTIC>0$. However, in Definition 2, a C-process is informationally closed to the microscopic universe process $X$. This implies C-process is also informationally closed to any other coarse-grainings of X including E (see also our reply to Q2). Therefore, only completely closed NTIC processes are consider as C-processes. 
    		Regarding the video camera example, please see more discussion in our reply to your Q6. \\

@@

        \begin{ans}        	
            The C-processes are constructed to answer questions about the scale problem of consciousness. Their definition therefore states their relation to the microscopic scale $X$. 
            At the same time it would be possible to remove $X$ from the definition and instead require that $Y$ is informationally closed with respect to all other processes. In some cases such a definition would be more general than the present one for example when there is no final microscale and instead there is an infinite number of more and more microscopic scales. However, we find the use of an explicit microscale $X$ easier to understand and sufficient to communicate the idea. Note that closure with respect to $X$ (if it exists) implies closure with respect to every coarse-graining of $X$.   
            To see this note that the information transfer from any coarse-graining (including $E$ and $S$) of $X$ to $Y$ must be lower than that from $X$ to $Y$, i.e. $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; S_t|Y_t)$ and $I(Y_{t+1}; X_t|Y_t) \geq I(Y_{t+1}; E_t|Y_t)$. So that $Y$ is informationally closed with respect to $X$ implies that $Y$ is also informationally closed with respect to $S, E$, and all other coarse-grainings of $X$.
        \end{ans}

@@

        process:$X$
        p(x'|x):=\delta_{f(x)}(x')-\delta_{\X\backslash f(x)}(|\X|-1)*n
        p(x'|x,n)=
        then H(X'|X)=H(\Epsilon)

        find g:\X \rightarrow \Y

        such that H(g(X')|g(X))=0
        but still H(g(X'))>0
        \begin{question}
            Exclusion or no exclusion? The authors state multiple times that "every process with a positive non-trivial information closure (NTCI) has consciousness." (p.3, and also p.12).
            a) Yet, Figure 4 is ambiguous in the sense that the maximum somehow seems important, while actually all levels should give rise to separate experiences. I don't see how ICT without something like exclusion (IIT style) would indicate that the maximum should correspond to human consciousness. It could just be any one out of many consciousnesses.
            b) p. 14: comparison to IIT: what does ICT say about different sets of variables at the same level. There might well be multiple ways to partition $X$ into S and E, with many overlapping S's. Would those all be conscious? They would not be informationally closed from each other but they could all fulfill the requirements in the Hypothesis. It seems like finding the maximum within a level over the possible sets of elements/variables is a necessary step to identify boundaries (I think also Krakauer does that across sets of variables, but not 100\% sure)        
        \end{question}

    	\begin{ans}
            We can see how Figure 4 was ambiguous with respect to this question. We do not impose the exclusion criterion in ICT and have changed Figure 4 to remove the impression that it does. 
            A key feature of ICT is that, instead of imposing the exclusion criterion, the concept of informational closure itself already involves the notion of system-environment separation and a boundary of a system \citep{BERTSCHINGER.2006}. For example, \citet{krakauer2014information,krakauer2020information} proposed an algorithm to add and remove variables in order to find the boundary. \\
            It is true that NTIC can be computed for every subset of a system and can also have a positive value of NTIC for multiple of those. However, according to our definition, if these processes are not informationally closed to their environments (including the complement subset in the system), ICT claims that they are not C-processes, and thus not conscious. . In order to find whole or entire consciousnesses we can use the algorithm in \citet{krakauer2014information, krakauer2020information}. This algorithm adds variables to or removes variables from the system if this results in a reduction of transfer entropy from the corresponding environment. This means that consciousnesses are informationally closed subsets of variables.

            This is also why ICT allowed the existence of multiple consciousnesses across the scales of coarse-graining. Because conscious processes are informationally closed from each other across the scale of coarse-graining, they are not able to know the existence of other consciousnesses within the same system (information flow from other processes is zero). This is in line with using informational closure in level identification \citep{PFANTE.2014}.
    	\end{ans}

@@

        \begin{ans}
        	The reviewer is right. Feed-forward networks can be conscious under ICT. We thank the reviewer to correct this point. Similarly, a video camera can achieve positive levels of NTIC and, therefore, be conscious. We have worked extensively on Section 5 to make this clear (see from Line:~\lineref{line:notIC}).
        	There we have weakened multiple claims involving a clear conscious to unconscious distinction to claims about differences between levels of consciousness. 
        	Concerning the camera example we can show that for a camera system filming an environment for which the mutual information from one step to the next is higher than the mutual information between one camera image and the next there are systems that achieve higher NTIC. 
        	For the case of the feedforward network we speculate that a similar situation remains true and that there are always systems that achieve higher levels of consciousness than those consisting only of feedforward networks.

@@

@@

    	\begin{ans}
	    	We want to emphasise that not all the processes in the neural system are NTIC processes, since some processes in the neural system are not informationally closed.
	    	To the conscious (NTIC) process, the rest of the neural system is considered as part of the environment. This notion is shortly indicated at line \lineref{line:neu-env} in our original manuscript. There is no doubt that these processes are still active during sleep and dreaming. We speculate that, during dreaming, the neural system can stably form the NTIC process with respect to its environment, i.e. other parts of the neural system.  However, at the current stage, this is mere speculation so we restrained ourself from making the statement in our manuscript. However, we thank the reviewer for bringing up this important question. We believe that this is still worth mentioning. We have added a short paragraph as follows:
